Supplementary Materials

### 2020-09-11 analysis/analysis.Rmd
some house-keeping

## EEG Data

Importing the primary EEG data set. This is odd-harmonic filtered data from region-of-interest consisting of six electrodes over occipital cortex.

```{r, fig.cap = "RMS data from two of the wallpaper groups, P2 and P4M. Odd harmonics are shown in A and B, while even harmonic data are shown in C and D, and occipital and parietal regions of interest are shown in dark nad light gray, respectively. The two groups elicit very different response amplitudes for odd harmonics over occipital cortex, but for even harmonics those differences are much less pronounced."}
plt <- cowplot::ggdraw() +
  cowplot::draw_image("../figures/occTopo_merged.png")
print(plt)

@@

In addition to the primary EEG data set, we are also importing two control data sets which are (a) even harmonic data from the same occipital electrodes, and (b) odd harmonic data from six parietal electrodes (see Figure 1.1 and the main paper).

@@

*  Use weakly-informative priors.
*  Fit a multi-level model using the lognormal distribution.
  + independent variable (wallpaper group) and one dependent variable (rms or threshold).
  + maximal random effect structure.
* Check model fit (r̂ statistics and trace plots).
* Extract mcmc samples from the posterior distributions.
* Use these samples to estimate the difference between sub- and super-groups.

@@

### Fit Model to EEG Data

@@

We will now compute the difference between sub- and super-groups.

@@

## Primary EEG Data

Finally, we calculate the probability that the RMS difference between subgroup and super-group is larger than zero given the data. This information is then binned so we can colour in the posterior density plots.

@@

```{r, fig.height=8, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero.", warning=FALSE}

@@

```{r ,fig.height=8, fig.cap="Distributions of the difference in mean log display duration threshold between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being less than zero.", warning=FALSE}

@@

## Control EEG Data

@@

```{r fig.height=8, echo = FALSE, fig.cap="Distributions of the difference in mean log(rms) between sub- and super-groups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero.", warning=FALSE}

@@

df %>% gather("measurement", "number", -p) %>%
  mutate(proportion = number/nrow(subgroups)) %>%
  ggplot(aes(x = p, y = proportion, colour = measurement)) + 
  geom_path(size = 1.5) +
  theme_minimal() + 
  ggthemes::scale_color_ptol(labels = c("primary EEG", "sensor control EEG", "harmonic control EEG", "psychophysical threshold")) +
  theme(legend.justification=c(0,0), legend.position=c(0,0), legend.background = element_rect()) +
  scale_y_continuous(limits = c(0, 1)) +
  xlab("probability of difference given data") + ylab("proportion of subgroup comparisons")

@@

If we take $p$=0.95 as our cut-off, we can see that the subgroup relations are preserved in 56/63 = 89% and 49/64 = 78% of the comparisons for the primary EEG and display durations repectively. This compares to the 32/64= 50% and 22/64 = 35% for the control EEG conditions.

@@

First of all, we run for the eeg rms data.

@@

## Correlation Between Primary EEG data and Psychophysical Thresholds

Finally, we will investigate whether there is a correlation between the our primary EEG measure (rms amplitude of odd harmonics over occipital cortex) and our display duration thresholds. As our two different measures come from different samples of participants, we are unable to do a direct comparison. However, we can use the results of the models discussed in Section 3 and check for a correlation between the predicted values of the two measures.

>>>>

## SSVEP Data

Importing the primary SSVEP data set. This is odd-harmonic filtered data from region-of-interest consisting of six electrodes over occipital cortex.

```{r, fig.cap = "SSVEP RMS data from two of the wallpaper groups, P2 and P4M. Odd harmonics are shown in A and B, while even harmonic data are shown in C and D, and occipital and parietal regions of interest are shown in dark nad light gray, respectively. The two groups elicit very different response amplitudes for odd harmonics over occipital cortex, but for even harmonics those differences are much less pronounced."}
plt <- cowplot::ggdraw() +
  cowplot::draw_image("../figures/occTopo_merged.png")
print(plt)

@@

In addition to the primary SSVEP data set, we are also importing two control data sets which are (a) even harmonic data from the same occipital electrodes, and (b) odd harmonic data from six parietal electrodes (see Figure 1.1 and the main paper).

@@

*  Use weakly-informative priors.
*  Fit a multi-level model using the lognormal distribution.
  + independent variable (wallpaper group) and one dependent variable (rms or threshold).
  + maximal random effect structure.
* Check model fit (r̂ statistics and trace plots).
* Extract mcmc samples from the posterior distributions.
* Use these samples to estimate the difference between sub- and supergroups.

@@

### Fit Model to SSVEP Data

@@

We will now compute the difference between sub- and supergroups.

@@

## Primary SSVEP Data

Finally, we calculate the probability that the SSVEP RMS difference between subgroup and supergroup is larger than zero given the data. This information is then binned so we can colour in the posterior density plots.

@@

```{r, fig.height=8, fig.cap="Distributions of the difference in mean log(rms) between sub- and supergroups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero.", warning=FALSE}

@@

```{r ,fig.height=8, fig.cap="Distributions of the difference in mean log display duration threshold between sub- and supergroups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being less than zero.", warning=FALSE}

@@

## Control SSVEP Data

@@

```{r fig.height=8, echo = FALSE, fig.cap="Distributions of the difference in mean log(rms) between sub- and supergroups. The index of each relationship is indicated by the colour of the y-axis label. The fill of the density plots indicated the probability of the difference being greater than zero.", warning=FALSE}

@@

df %>% gather("measurement", "number", -p) %>%
  mutate(proportion = number/nrow(subgroups)) %>%
  ggplot(aes(x = p, y = proportion, colour = measurement)) + 
  geom_path(size = 1.5) +
  theme_minimal() + 
  ggthemes::scale_color_ptol(labels = c("primary SSVEP", "sensor control SSVEP", "harmonic control SSVEP", "psychophysical threshold")) +
  theme(legend.justification=c(0,0), legend.position=c(0,0), legend.background = element_rect()) +
  scale_y_continuous(limits = c(0, 1)) +
  xlab("probability of difference given data") + ylab("proportion of subgroup comparisons")

@@

If we take $p$=0.95 as our cut-off, we can see that the subgroup relations are preserved in 56/63 = 89% and 49/64 = 78% of the comparisons for the primary SSVEP and display durations repectively. This compares to the 32/64= 50% and 22/64 = 35% for the control SSVEP conditions.

@@

First of all, we run for the SSVEP RMS data.

@@

## Correlation Between Primary SSVEP data and Psychophysical Thresholds

Finally, we will investigate whether there is a correlation between the our primary SSVEP measure (RMS amplitude of odd harmonics over occipital cortex) and our display duration thresholds. As our two different measures come from different samples of participants, we are unable to do a direct comparison. However, we can use the results of the models discussed in Section 3 and check for a correlation between the predicted values of the two measures.
